NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-18 ms_nihao_budget.tex
rephrase the statement about the situation of emission and absorption observation

\subsection{Comparison with Observations of Milky Way mass haloes}
Since the CGM is too diffuse to create emission lines, it must be
observed using quasar absorption lines.  The COS-HALOs survey is
filling in details about the $z \sim 0$ CGM \citep{Peeples14,
  Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.  For the CGM of
low-redshift $\sim L^*$ galaxies ($\Mstar\sim 10^{10.5}\Msun$),
\citet{Tumlinson13} and \citet{Peeples14} constrain the mass of  the
warm-hot CGM ($T \sim 10^{5-7}$K), \citet{Werk14} provides a strict
lower limit to the mass of cool material ($T \sim 10^{4-5}$K) in the
CGM of these galaxies.  In a study using X-rays,  \citet{Anderson13}
place a constraints on the mass of  hot gas ($T > 10^7$K) residing in
the extended hot halos.

@@

>>>>

\subsection{Comparison with Observations of Milky Way mass haloes}
{\bf Observations can gain information of CGM from absorption lines
and emission lines. Although emission lines allow us to direct obtain
a 3D picture of the distribution of gas in the CGM, emission line studies
preferentially probe the dense gas closer to galaxies since gas 
emissivity scales with the square of density. The situation is changing
by building current facilities, e.g.\citet{Hayes16}, absorption line,
however, is the most common observational constraints on the physical
state of the CGM.}
The COS-HALOs survey is
filling in details about the $z \sim 0$ CGM \citep{Peeples14,
  Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.  For the CGM of
low-redshift $\sim L^*$ galaxies ($\Mstar\sim 10^{10.5}\Msun$),
\citet{Tumlinson13} and \citet{Peeples14} constrain the mass of  the
warm-hot CGM ($T \sim 10^{5-7}$K), \citet{Werk14} provides a strict
lower limit to the mass of cool material ($T \sim 10^{4-5}$K) in the
CGM of these galaxies.  In a study using X-rays,  \citet{Anderson13}
place a constraints on the mass of  hot gas ($T > 10^7$K) residing in
the extended hot halos.

@@

% O VI Emission Imaging of a Galaxy with the Hubble Space Telescope: a Warm Gas Halo Surrounding the Intense Starburst SDSS J115630.63+500822.1O VI Emission Imaging of a Galaxy with the Hubble Space Telescope: a Warm Gas Halo Surrounding the Intense Starburst SDSS J115630.63+500822.1
\bibitem[Hayes et al.(2016)]{Hayes16}
Hayes, M., Melinder, J., {\"O}stlin, G., et al.\ 2016, arXiv:1606.04536
